The \dealii{} Library, Version 9.0

### 2018-04-05 9.0/paper.tex
add myself, fix trailing whitespace and one bibtex reference
Some small changes.

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Timo Heister,
  },
  pdftitle={The deal.II Library, Version 9.0, 2018},
}

@@

% \author[2]{Wolfgang Bangerth}
% \affil[2]{Department of Mathematics, Colorado State University, Fort
%   Collins, CO 80523-1874, USA.
%     {\texttt{bangerth@colostate.edu}}}
% 
% \author[3]{Denis Davydov}
% \affil[3]{Chair of Applied Mechanics, University of
%      Erlangen-Nuremberg, Egerlandstr.\ 5, 91058 Erlangen, Germany.
%     {\texttt{denis.davydov@fau.de}}}

\author[4]{Timo Heister}
\affil[4]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
% 
% \author[5]{Luca Heltai}
% \affil[5]{SISSA,
%   International School for Advanced Studies,
%   Via Bonomea 265,
%   34136, Trieste, Italy.
% {\texttt{luca.heltai@sissa.it}}}
% 
% \author[6]{Martin Kronbichler}
% \affil[6]{Institute for Computational Mechanics,
%   Technical University of Munich,
%   Boltzmannstr.~15, 85748 Garching, Germany.
%   {\texttt{kronbichler@lnm.mw.tum.de}}}
% 
\author[7]{Matthias Maier}
\affil[7]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA.
  {\texttt{msmaier@umn.edu}}}
% 
% \author[8]{Jean-Paul Pelteret}
% \affil[8]{Chair of Applied Mechanics,
%   University of Erlangen-Nuremberg,
%   Egerlandstr.\ 5,
%   91058 Erlangen,
%   Germany.
%   {\texttt{jean-paul.pelteret@fau.de}}}
% 
 \author[9]{Bruno Turcksin\footnote{
   This manuscript has been authored by UT-Battelle, LLC under Contract No.
   DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
   Government retains and the publisher, by accepting the article for
   publication, acknowledges that the United States Government retains a
   non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
   the published form of this manuscript, or allow others to do so, for United
   States Government purposes. The Department of Energy will provide public
   access to these results of federally sponsored research in accordance with the
   DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
 \affil[9]{Computational Engineering and Energy Sciences Group,
   Computional Sciences and Engineering Division,
   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
   TN 37831, USA.
   {\texttt{turcksinbr@ornl.gov}}}
% 
% \author[10]{David Wells}
% \affil[10]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
% Troy, NY 12180, USA.
%   {\texttt{wellsd2@rpi.edu}}}

@@

\item
  Support for Sundials

@@

@@

@@

\marginpar{update}
\dealii{} can interface with many other libraries:
\begin{multicols}{2}
\begin{itemize}
\item ARPACK \cite{arpack}
\item BLAS, LAPACK
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item SLEPc \cite{Hernandez:2005:SSF}
\item Threading Building Blocks \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

@@

% W.~Bangerth was partially
% supported by the National Science Foundation under award OCI-1148116
% as part of the Software Infrastructure for Sustained Innovation (SI2)
% program; and by the Computational Infrastructure in Geodynamics initiative
% (CIG), through the National Science Foundation under Awards
% No.~EAR-0949446 and EAR-1550901 and The University of California -- Davis.
% 
% D.~Davydov was supported by the European Research Council (ERC) through the Advanced Grant 289049 MOCOPOLY and the Competence Network for Technical and Scientific High Performance Computing in Bavaria (KONWIHR).

@@

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Denis Davydov,
    Timo Heister,
    Luca Heltai,
    Matthias Maier
  },
  pdftitle={The deal.II Library, Version 9.0, 2018},
}

@@

\author[2]{Wolfgang Bangerth}
\affil[2]{Department of Mathematics, Colorado State University, Fort
  Collins, CO 80523-1874, USA.
    {\texttt{bangerth@colostate.edu}}}

\author[3]{Denis Davydov}
\affil[3]{Chair of Applied Mechanics, University of
     Erlangen-Nuremberg, Egerlandstr.\ 5, 91058 Erlangen, Germany.
    {\texttt{denis.davydov@fau.de}}}

\author[4]{Timo Heister}
\affil[4]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
%
\author[5]{Luca Heltai}
\affil[5]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy.
{\texttt{luca.heltai@sissa.it}}}
%
% \author[6]{Martin Kronbichler}
% \affil[6]{Institute for Computational Mechanics,
%   Technical University of Munich,
%   Boltzmannstr.~15, 85748 Garching, Germany.
%   {\texttt{kronbichler@lnm.mw.tum.de}}}
%
\author[7]{Matthias Maier}
\affil[7]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA.
  {\texttt{msmaier@umn.edu}}}

\author[8]{Jean-Paul Pelteret}
\affil[8]{Chair of Applied Mechanics,
  University of Erlangen-Nuremberg,
  Egerlandstr.\ 5,
  91058 Erlangen,
  Germany.
  {\texttt{jean-paul.pelteret@fau.de}}}

 \author[9]{Bruno Turcksin\footnote{
   This manuscript has been authored by UT-Battelle, LLC under Contract No.
   DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
   Government retains and the publisher, by accepting the article for
   publication, acknowledges that the United States Government retains a
   non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
   the published form of this manuscript, or allow others to do so, for United
   States Government purposes. The Department of Energy will provide public
   access to these results of federally sponsored research in accordance with the
   DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
 \affil[9]{Computational Engineering and Energy Sciences Group,
   Computional Sciences and Engineering Division,
   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
   TN 37831, USA.
   {\texttt{turcksinbr@ornl.gov}}}
%
% \author[10]{David Wells}
% \affil[10]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
% Troy, NY 12180, USA.
%   {\texttt{wellsd2@rpi.edu}}}

@@

\item
  Support for Sundials and ROL

@@

\item 
  Support for Nanoflann

\item 
  Support for Assimp

\item 
  Initial support for GMHS

@@

\subsection{New non-standard quadrature rules}

\begin{itemize}
\item QSimplex
\item QDuffy
\item QTrianglePolar
\item QSplit
\end{itemize}

Mostly used for BEM problems.

@@

\marginpar{update}
\dealii{} can interface with many other libraries:
\begin{multicols}{2}
\begin{itemize}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS, LAPACK
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item Threading Building Blocks \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

@@

% W.~Bangerth was partially
% supported by the National Science Foundation under award OCI-1148116
% as part of the Software Infrastructure for Sustained Innovation (SI2)
% program; and by the Computational Infrastructure in Geodynamics initiative
% (CIG), through the National Science Foundation under Awards
% No.~EAR-0949446 and EAR-1550901 and The University of California -- Davis.
%
D.~Davydov was supported by the German Science Foundation
(Deutsche Forschungs-Gemeinschaft, DFG), grant DA 1664/2-1.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
